### 2021-09-23 documentos/math.tex
lolwhat?

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\mu}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\mu=0}^{3} \alpha_{\mu} \ket{\sigma_{\mu}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \dyad{\sigma_{\mu}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\mu}}}{{\sigma_{\mu'}}} = \tr \left(\sigma_{\mu}^{\dagger} \sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$. After some steps it is possible to show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \sigma_{\mu} \otimes \sigma_{\mu}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\mu}=\sqrt{\frac{\tau_{\mu}}{2}}\sigma_{\mu}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\nu} = \frac{1}{2}\sum_{\mu=0}^3H_{\nu\mu}^{(4)}\tau_{\mu},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}
% 
(Proofs in an appendix using binary indices XD)

@@

>>>>

We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\mu}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel. By writing the density matrix in vector form $\ket{\rho}=\sum_{\mu=0}^{3} \alpha_{\mu} \ket{\sigma_{\mu}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
% 
\begin{equation}
\hat{\mathcal{E}} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \dyad{\sigma_{\mu}},
% \label{Map_Pauli}
\end{equation}
%
where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of
the Pauli basis and satisfy the usual relation $
\braket{{\sigma_{\mu} }}{{\sigma_{\mu'} }} = \tr \left(\sigma_{\mu}^{\dagger}
\sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$. After some steps it is possible to
show that the associated Choi matrix reads
% 
\begin{equation}
 \mathcal{D} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \sigma_{\mu} \otimes \sigma_{\mu}^*.
%  \label{Choi_1}
\end{equation}
% 
Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\mu}=\sqrt{\frac{\tau_{\mu}}{2}}\sigma_{\mu}$. For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
% 
\begin{equation}
 \lambda_{\nu} = \frac{1}{2}\sum_{\mu=0}^3H_{\nu\mu}^{(4)}\tau_{\mu},
\end{equation}
%
or
% 
\begin{equation}
 \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
\end{equation}
% 
where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
% 
\begin{equation}
 H^{(2)}=\begin{pmatrix}
        1 & 1\\
        1 & -1\\
    \end{pmatrix}.
 \label{Hadd_Mat}
\end{equation}
% 
(Proofs in an appendix using binary indices XD)

@@

The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vec \tau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a positive vector $\vec p$. In compontents, this would read 
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
\sa_{\alpha_N\beta_N}$. From the

It results convenient to express the 
previous equation in

### 2021-09-23 documentos/pce.tex
traza
oops, forgot to add the file
lolwhat?

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
cuando hayamos escrito lo de un qubit}. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$. Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
 \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia} \ddnote{De momento no he encontrado alguna reference, para qubits si, pero para los generales no, estoy checando de nuevo el paper de Ruskai para entender que tanto se solapan, a ver si puedo decir algo}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

@@

\begin{figure} % {{{
\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
\pgfmathsetmacro{\unitstep}{5.8}
\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
\node at (-0.6,0.5) {(a)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{\y,\x}$}};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
\node at (-0.6,0.5) {(b)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
\node at (-0.6,0.5) {(c)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
	\caption{In (a) we introduce the
positions of two qubit diagrams. The diagrams in 
(b) corresponds to a quantum channel that results from the tensor product of
bit flip channels in each qubit [see \fref{fig:one:qubit:examples}(c)],
and in (c) a diagram of a map that is not a quantum channel is presented.}
	\label{fig:two:qubit:examples}
\end{figure} % }}}

>>>>

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
%             \quad r_{\vec0}=1,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=2^N\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

@@

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$. Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
 \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases. También debemos tener un nombre pues lo de la diagonazliación funciona
para eso y quizá también seran relevantes para la parte de decoherencia}
\ddnote{De momento no he encontrado alguna reference, para qubits si, pero para
los generales no, estoy checando de nuevo el paper de Ruskai para entender que
tanto se solapan, a ver si puedo decir algo}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

@@

\begin{figure} % {{{
\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
\pgfmathsetmacro{\unitstep}{5.2}
\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
\node at (-0.5,0.5) {(a)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(b)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(c)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
	\caption{In (a) we introduce the
positions of two qubit diagrams. The diagrams in 
(b) corresponds to a quantum channel that results from the tensor product of
bit flip channels in each qubit [see \fref{fig:one:qubit:examples}(c)],
and in (c) a diagram of a map that is not a quantum channel is presented.}
	\label{fig:two:qubit:examples}
\end{figure} % }}}
